Scalar on Function Regression

### 2022-01-02 Presentation/slides.tex
Increment
More FPCA stuff

		\begin{multicols}{2}
			\begin{enumerate}
				\item $\mathbb{E}[\xi_i(\omega)] = 0$
				\item $var(\xi_i(\omega)) = \lambda_i$
				\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
			\end{enumerate}
		\end{multicols}
	\end{frame}

	\begin{frame}{Principal Component Analysis}
		$\Sigma_X$ unknown $\rightarrow$ \textbf{sample analogues}

		\begin{itemize}
			\item Let $\mathbf{X} \in \mathbb{R}^{n \times p}$ be the matrix containing the standardized regressors in the usual configuration.
			\item Let $\hat{\Sigma}_X = \frac{\mathbf{X}'\mathbf{X}}{n}$
			\item Let $\{\hat{\gamma}_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\hat{\Sigma}_X$
			\item Let $\{\hat{\lambda}_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\hat{\Sigma}_X$
		\end{itemize}

@@

		Where the $\xi_j$ are scalar-valued random variables with the following properties.
		\begin{multicols}{2}
			\begin{enumerate}
				\item $\mathbb{E}[\xi_i(\omega)] = 0$
				\item $var(\xi_i(\omega)) = \lambda_i$
				\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
			\end{enumerate}
		\end{multicols}

@@

>>>>

		\begin{multicols}{2}
			\begin{enumerate}
				\item $\mathbb{E}[\xi_i(\omega)] = 0$
				\item $Var(\xi_i(\omega)) = \lambda_i$
				\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
			\end{enumerate}
		\end{multicols}
	\end{frame}

@@

		Where the $\xi_j$ are scalar-valued random variables with the following properties.
		\begin{multicols}{2}
			\begin{enumerate}
				\item $\mathbb{E}[\xi_i(\omega)] = 0$
				\item $Var(\xi_i(\omega)) = \lambda_i$
				\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
			\end{enumerate}
		\end{multicols}

@@

	\begin{frame}{Principal Component Analysis}
		A related concept is \textbf{Principal Component Analysis} (PCA).
		\vspace{0.2cm}

		$\Sigma_X$ unknown $\rightarrow$ \textbf{sample analogues}

		\begin{itemize}
			\item Let $\mathbf{X} \in \mathbb{R}^{n \times p}$ contain the standardized regressors
			\item Let $\hat{\Sigma}_X = \frac{\mathbf{X}'\mathbf{X}}{n}$
			\item Let $\{\hat{\gamma}_i \: \vert \: i = 1, \dots, p\}$ be the orthonormal \textbf{Eigenvectors} of $\hat{\Sigma}_X$
			\item Let $\{\hat{\lambda}_i \: \vert \: i = 1, \dots, p\}$ be the corresponding \textbf{Eigenvalues} of $\hat{\Sigma}_X$
		\end{itemize}
		\vspace{0.2cm}

		Then $Z_i(\omega) = \hat{\gamma}_i' X(\omega)$ is called the i'th principal component and
		\begin{multicols}{2}
			\begin{enumerate}
				\item $\mathbb{E}[Z_i(\omega)] = 0$
				\item $Var(Z_i(\omega)) = \hat{\lambda}_i$
				\item $Cov(Z_i(\omega), Z_j(\omega)) = 0$ for $i \neq j$
			\end{enumerate}
		\end{multicols}
	\end{frame}

	\begin{frame}{Functional Principal Component Analysis}
		This idea can be extended to functional regressors in the form of \textbf{Functional Principal Component Analysis} (FPCA).
		\vspace{0.2cm}

		\textbf{Empirical Mean Function}:
		$$\hat{\mu}(t) = \frac{1}{n}\sum_{j = 1}^{n}f_j(t)$$

		\textbf{Empirical Autocovariance Function}:
		$$\hat{c}(t,s) = \frac{1}{n} \sum_{j = 1}^{n} \left(f_j(t) - \hat{\mu}(t)\right) \left(f_j(s) - \hat{\mu}(s)\right)$$

	\begin{frame}{Functional Principal Component Analysis}

		The \textbf{Eigenvalues} and \textbf{Eigenfunctions}: $\{(\hat{\lambda}_i, \hat{\nu}_i) \: \vert \: i \in \mathcal{I}\}$  are solutions of the following equation:
		$$ \int_{0}^{1}\hat{c}(t,s)\hat{\nu}(s) \mathrm{d}s = \hat{\lambda} \hat{\nu}(t) $$
		\vspace{0.2cm}

		The principal components are then defined analogously to before:
		$$Z_j(\omega) = \int_{0}^{1} (F(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$
